---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![ORCiD](https://img.shields.io/badge/ORCiD-0000--0001--7879--4531-green.svg)](http://orcid.org/0000-0001-7879-4531)

# irmass - Independent race model analysis of selective stopping

## Compendium URL

## Author
Bram Zandbelt (bramzandbelt@gmail.com)

## Contentes
This repository contains the research compendium 


The compendium contains all data, code, and text associated with the following paper

```
Paper bibliometrics go here
```

The paper is available in two formats:
- the Open Access preprint, before submission
- the final published copy is available on (subscription-only) site of ...


Why should I use it?
How do I use it?
How do I get it?

### Data

File names consist of:
- data category
  - analysis_inputs
  - analysis_outputs
- notebook name
  
- primary content
  - `bf`: bayes factors
  - `rt`: response times
  - `resp`: response data
  - `fig`: figure
  - `param`: model parameters
  - `prd`: model predictions
  - `desc`: descriptive statistics


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```


## Licenses

Manuscript: CC-BY-4.0

Code: MIT 

Data:

## R Session Information

## Notes

The organization of this research compendium was inspired by the following sourced:
- [Hadley Wickham's book "R Packages"](https://r-pkgs.had.co.nz/), 
- the Github repository [Reproducible Research R Package](https://github.com/ropensci/rrrpkg)
- Ben Marwick's [research compendium of the 1989 excavation report Madjebebe](https://github.com/benmarwick/1989-excavation-report-Madjebebe) 
