---
params:
  title: "04_individual_analysis_rt_difference_nosignal_stoprespond"
title: "`r stringr::str_to_title(params$title)`"
author: "Bram B. Zandbelt"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true 
    number_sections: true
    depth: 4
    df_print: paged
    theme: readable
    highlight: pygments
---

```{r setup, include=FALSE}
# Set root dir to project directory to ensure that code is always run relative to the project directory, no matter if it is run using `knitr` or interactively.
knitr::opts_knit$set(root.dir = rprojroot::find_root(rprojroot::has_file("DESCRIPTION")))

# Attach tideverse package to enable access to pipe (%>%)
require(tidyverse)
```

# Overview
This notebook covers Analysis 2 of the pre-registration (https://osf.io/mq64z/), investigating the difference between no-signal and stop-respond RT at the individual level.

# Preliminaries

## Identify the project directory
All paths in the code are relative to the project directory.
```{r Define project directory}
project_dir <- rprojroot::find_root(rprojroot::has_file("DESCRIPTION"))
```

## Verify existence of output directories
```{r Define and verify existence of output directories}

derivatives_dir <- file.path(project_dir,"data","derivatives")
figures_dir <- file.path(project_dir, "figures")
notebook_name <- params$title

irmass::verify_output_dirs(base_dirs = list(derivatives_dir, figures_dir),
                           notebook_name = notebook_name)
```

# Read data

## Tidied and criteria-checked trial data from experiment session

```{r Read preprocessed trial response time data from experimental session}
(expt_trial_rt_data <-
  readr::read_csv(file.path(derivatives_dir, 
                            "02_assess_task_performance_criteria", 
                            "tidy_expt_trial_rt_data_for_analysis.csv"),
                  col_types = irmass::get_col_types("expt_trial_rt_data")
                  )
  )
```

# Data cleaning and processing

```{r Filter out irrelavant rows and columns}
(cleaned_trial_level_data <- 
   
   expt_trial_rt_data %>%
   
   # Keep relevant trials only -------------------------------------------------
 
   # Responses that are:
   
   # ... non-anticipatory
   dplyr::filter(RT_trial > 0.150) %>%
   
   # ... bimanual
   dplyr::filter(r == "RB") %>%
   
   # ... no-stop or stop-signal
   dplyr::filter(trial_alt %in% c('SAS', 'SSS', 'NS')) %>%
   
   # Compute inverse of RT ------------------------------------------------------
  
   # This is the dependent variable in the analysis
   dplyr::mutate(RT_trial_inv = 1 / RT_trial) %>%
   
   # Keep relevant columns only -------------------------------------------------
   
   dplyr::select(subjectIx, trial_alt, RT_trial, RT_trial_inv) %>%
   
   # Ensure that subjectIx is coded as a factor (for plotting) ------------------
   dplyr::mutate(subjectIx = factor(subjectIx))
 
)
```

## Analysis inputs
Action-selective stopping
```{r Define analysis inputs - action-selective stopping}
(analysis_inputs_sas <- 
   cleaned_trial_level_data %>% 
   dplyr::filter(trial_alt %in% c('SAS','NS')) %>% 
   droplevels()
 )
```

Stimulus-selective stopping
```{r Define analysis inputs - stimulus-selective stopping}
(analysis_inputs_sss <- 
   cleaned_trial_level_data %>% 
   dplyr::filter(trial_alt %in% c('SSS','NS')) %>% 
   droplevels()
 )
```

# Inferential statistics

## Action-selective stopping
Prediction of $H_0$: action-selective stop-respond response times are _not_ shorter than no-stop response times
Prediction of $H_1$: action-selective stop-respond response times are shorter than no-stop response times

```{r}
(analysis_outputs_sas <- 
  irmass::test_srrt_vs_nsrt_idv(tibb = analysis_inputs_sas,
                                trial_alt_levels = c('SAS','NS')
                                )
 )
```

## Stimulus-selective stopping
Prediction of $H_0$: stimulus-selective stop-respond RT $\not<$ no-signal RT
Prediction of $H_1$: stimulus-selective stop-respond RT < no-signal RT

```{r}
(analysis_outputs_sss <- 
  irmass::test_srrt_vs_nsrt_idv(tibb = analysis_inputs_sss,
                                trial_alt_levels = c('SSS','NS')
                                )
 )
```
  
# Data visualization

## Action-selective stopping
```{r, out.width='100%'}
(plt_sas <- irmass::plot_srrt_vs_nsrt_idv(trial_data = analysis_inputs_sas,
                                          bf_data = analysis_outputs_sas,
                                          plot_orientation = 'horizontal')
 )
```

Figure title
```{r Define figure title - action-selective stopping}
plt_sas_title <- 'Response times on action-selective stop-respond trials and no-signal trials.'
```

Figure description
```{r Define figure description - action-selective stopping}
plt_description <- 'Each panel shows data from one participant, including (i) response time distirbutions on individual stop-respond trials and no-signal trials, displayed as violin scatter plots (each asterisk is a trial); (ii) mean response time across trials, indicated by white, filled circles; (iii) the Bayes factor quantifying the evidence for $H_0$ vs $H_1$ ($B_{01}$), indicated by the panel background color; (iv) the subject identifier, indicated by the number in the top-right corner. Panels are ordered by $B_{01}$ (descending order).'
```

## Stimulus-selective stopping
```{r, out.width='100%'}
(plt_sss <- irmass::plot_srrt_vs_nsrt_idv(trial_data = analysis_inputs_sss,
                                          bf_data = analysis_outputs_sss,
                                          plot_orientation = 'horizontal'
                                          )
 )
```

Figure title
```{r Define figure title - stimulus-selective stopping}
plt_sss_title <- 'Response times on stimulus-selective stop-respond trials and no-signal trials.'
```

# Write data

## Analysis input data

### Action-selective stopping
```{r Write to disk - analysis input data action-selective stopping}
readr::write_csv(analysis_inputs_sas,
                 path = file.path(derivatives_dir, 
                                  notebook_name, 
                                  paste('analysis_inputs',
                                        notebook_name,
                                        'action_selective_stopping',
                                        'rt_data.csv', 
                                        sep = '_')
                                  ),
                 col_names = TRUE)
```

### Stimulus-selective stopping
```{r Write to disk - analysis input data stimulus-selective stopping}
readr::write_csv(analysis_inputs_sss,
                 path = file.path(derivatives_dir, 
                                  notebook_name, 
                                  paste('analysis_inputs',
                                        notebook_name,
                                        'stimulus_selective_stopping',
                                        'rt_data.csv', 
                                        sep = '_')
                                  ),
                 col_names = TRUE)
```


## Analysis output data
Bayes factors

### Action-selective stopping
```{r Write to disk - analysis output data action-selective stopping}
readr::write_csv(analysis_outputs_sas,
                 path = file.path(derivatives_dir, 
                                  notebook_name, 
                                  paste('analysis_outputs',
                                        notebook_name,
                                        'action_selective_stopping',
                                        'b01.csv', 
                                        sep = '_')
                                  ),
                 col_names = TRUE)
```

### Stimulus-selective stopping
```{r Write to disk - analysis output data stimulus-selective stopping}
readr::write_csv(analysis_outputs_sss,
                 path = file.path(derivatives_dir, 
                                  notebook_name, 
                                  paste('analysis_outputs',
                                        notebook_name,
                                        'stimulus_selective_stopping',
                                        'b01.csv', 
                                        sep = '_')
                                  ),
                 col_names = TRUE)
```


## Plotting input data

Consists of analysis input data and analysis output data, which are already written to disk.

## Plotting output data
Figures

### Action-selective stopping
```{r Write to disk - plot of action-selective stopping descriptive and inferential statistics}

# Figure
filename_plt_sas <- 
  paste('plot',
        notebook_name,
        'action_selective_stopping.pdf',
        sep = '_')

ggplot2::ggsave(plot = plt_sas,
                path = file.path(figures_dir, notebook_name),
                filename = filename_plt_sas,
                device = "pdf",
                width = 18,
                height = 13.5,
                units = 'cm'
                )

# Figure caption
irmass::write_fig_cap(
  fig_title = plt_sas_title, 
  fig_description = plt_description, 
  fig_dir = figures_dir, 
  notebook_name = notebook_name, 
  stopping_type = "action_selective")
```

### Stimulus-selective stopping
```{r Write to disk - plot of stimulus-selective stopping descriptive and inferential statistics}

# Figure
filename_plt_sss <- 
  paste('plot',
        notebook_name,
        'stimulus_selective_stopping.pdf',
        sep = '_')

cowplot::ggsave(plot = plt_sss,
                path = file.path(figures_dir, notebook_name),
                filename = filename_plt_sss,
                width = 18,
                height = 13.5,
                units = 'cm'
                )

# Figure caption
irmass::write_fig_cap(
  fig_title = plt_sss_title, 
  fig_description = plt_description, 
  fig_dir = figures_dir, 
  notebook_name = notebook_name, 
  stopping_type = "stimulus_selective")
```

# Upload data to figShare

```{r Upload data to figShare - plot of action-selective stopping descriptive and inferential statistics}
if (irmass::get_figshare_specs('do_upload')) {
  
  (article_id_plt_sas <- 
    rfigshare::fs_new_article(title = plt_sas_title,
                              description = plt_description,
                              type = 'figure',
                              authors = irmass::get_figshare_specs('authors'),
                              tags = irmass::get_figshare_specs('tags'),
                              links = irmass::get_figshare_specs('links'),
                              files = file.path(figures_dir, notebook_name, filename_plt_sas),
                              visibility = irmass::get_figshare_specs('visibility')
                              )
   )
}
```

```{r Upload data to figShare - plot of stimulus-selective stopping descriptive and inferential statistics}
if (irmass::get_figshare_specs('do_upload')) {
  
  (article_id_plt_sss <- 
    rfigshare::fs_new_article(title = plt_sss_title,
                              description = plt_description,
                              type = 'figure',
                              authors = irmass::get_figshare_specs('authors'),
                              tags = irmass::get_figshare_specs('tags'),
                              links = irmass::get_figshare_specs('links'),
                              files = file.path(figures_dir, notebook_name, filename_plt_sss),
                              visibility = irmass::get_figshare_specs('visibility')
                              )
   )
}
```
